Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-23 main.Rmd
till cyclic calendar algebra re-check and maintain consistency

Linear time granularities respect the linear progression of time such as hours, days, weeks and months, and non-repeating. One of the first attempts to characterize these granularities is due to @Bettini1998-ed. However, the definitions and rules defined are inadequate for describing cyclic or repeating granularities. Hence, there is a need to define some new cyclic time granularities, that can be useful in visualizations. Cyclic time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

The remainder of the paper is organized as follows: Section \ref{sec:linear-time} provide some background material on linear granularities and introduces calendar algebra for computing different linear granularities. Section \ref{sec:cyclic-gran} formally characterizes different cyclic time granularities by extending the framework of linear time granularities. Section \ref{sec:cyclic-calendar} introduces calendar algebra for computing cyclic time granularities. Section \ref{sec:data-structure} discusses the data structure for exploring the conditional distributions of the associated time series across pairs of cyclic time granularities. Section \ref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization. Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application. Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.

@@

<!-- CONTENT CUT -->
<!-- \begin{definition}[Finer than]\label{def:finerthan} -->
<!-- A linear granularity $G$ is finer than a linear granularity $H$, denoted $G \preceq H$, if for each index $i$, there exists an index $j$ such that $G(i) \subset H(j)$. -->
<!-- \end{definition}. -->

@@

For example, day $\trianglelefteq$ week since every granule of "week" is the union of some set of granules of "day". Consider another example where day $\trianglelefteq$ month. This relationship however is incomplete without its association to periodicity. Each month is a grouping of the same number of days over years, hence the period of the grouping (day, month) is one year, if leap years are ignored. The period becomes 400 years with the inclusion of leap years and all their exceptions.

@@

Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra [@Ning2002-tf]. It is assumed that there exists a _bottom granularity_ and calendar algebra operations are designed to generate new granularities recursively from the bottom one. Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} for illustrations in circular and aperiodic cyclic granularities.

@@

The altering-tick operation:
: Let $G_1$, $G_2$ be full-integer labeled granularities, and $l$, $k$, $m$ integers, where $G_2$ partitions $G_1$, and $1 \leq l \leq m$. The altering-tick operation $\text{Alter}^{m}_{l,k} (G_2, G_1)$ operation modifies the granules of $G_1$ so that the $l^{\text{th}}$ granule of each period has $k$ additional granules of $G_2$.

For example, due to the uneven length of months, we need to use the altering-tick operation to compute months from days. We can consider a granularity "pseudomonth" which computes months only for non-leap years by grouping 31 days, and then shrink April (4), June (6), September (9) and November (11) by 1 day, and shrink February (2) by 3 days [@Ning2002-tf]. For more variations of calendar algebra operations, see @Ning2002-tf.

@@

We propose a formalism of cyclic time granularities through the tsibble [@wang2019tsibble] data structure. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. <!--In a tsibble, each observation (row) is uniquely identified by index and key.--> A time domain, as defined by @Bettini1998-ed, is essentially a mapping of the index set to the time index of a tsibble. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the time index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble.<!--Consistent with the assumption of @Bettini2000-vy, all linear granularities can be generated from the bottom granularity by calendar algebraic operations.-->

Cyclic granularities can be constructed by relating two linear granularities. The mappings between these linear granularities could be _regular_ with every granule of coarser linear granularity being made up of same number of granules of finer linear granularity or _irregular_. <!--For example, a regular mapping exists between  (where 60 minutes always add up to 1 hour), while an irregular mapping exists between  (as the number of days per month ranges from 28 to 31). A grouping operation in Calendar algebra could lead to a regular mapping, whereas a altering-tick operation could result in an irregular mapping.--> Cyclic time granularities are referred to as **circular** if mappings are regular and **quasi-circular** if the mappings are irregular. Examples of common circular granularities include hour of the day, and day of the week, whereas examples for quasi-circular granularities can be day of the month or week of the month.

@@

\autoref{fig:circular-dow} depicts the circular granularity "Day-of-Week", constructed from linear granularities "day" (the bottom granularity) and "week". The granules that overlap share elements from the underlying time domain. In this example, $P=7$, and the circular granularity $C_{\text{day}, \text{week}}$ representing day-of-week consists of the repeated pattern $\{L(0), L(1), L(2),$ $L(3), L(4), L(5), L(6)\}$.

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
minute-of-hour: & $C_1$ & $= L_1(z \mod 60)$ & $P_1 =$&$60$ \\
minute-of-day: & $C_2$ & $= L_2(z \mod 60*24)$ & $P_2=$&$`r 60*24`$\\
hour-of-day: & $C_3$ & $= L_3(\lfloor z/60\rfloor\mod 24)$  & $P_3 =$&$24$ \\
hour-of-week: & $C_4$ & $= L_4(\lfloor z/60\rfloor\mod 24*7)$  & $P_4=$&$`r 24*7`$\\
day-of-week: & $C_5$ & $= L_5(\lfloor z/24*60\rfloor \mod 7)$ & $P_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative circular granularities with bottom granularity "minutes". These circular granularities relate two linear granularities one of which groups periodically into the other with regular mapping.}
\label{tab:definitions}
\end{table}

<!-- # ```{r tab-mayan} -->
<!-- # table_mayan <- tibble(`Circular granularity` = c("minute-of-hour","minute-of-day", -->
<!-- #                                                  "hour-of-day","hour-of-week", "day-of-week"), -->
<!-- #                       Expression = c($L_1(z \mod 60)$, L_2(z \mod 60*24), L_3(\lfloor z/60\rfloor\mod 24)$,  L_4(\lfloor z/60\rfloor\mod 24*7)$, L_5(\lfloor z/24*60\rfloor \mod 7)$)) -->
<!-- #                                                   -->
<!-- #                                                   -->
<!-- #                       C = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1), -->
<!-- #                       K = c(20, 18, 20, 20, 1))  -->
<!-- # kable(table_mayan,  -->
<!-- #       format = "latex", -->
<!-- #       caption = "Hierarchy table for Mayan calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All cyclic granularities are circular with $K$ as the period length.") -->
<!-- # ``` -->

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule

day-of-month: & $Q_1$ && $P_1 = 31, 30, 29, 28$\\
hour-of-month: & $Q_2$ && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
day-of-year: & $Q_3$ && $P_3 = 366, 365$\\
week-of-month: & $Q_4$ && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative quasi-circular granularities with potential period lengths. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping.
Illustrative quasi-circular granularities }
\label{tab:quasi}
\end{table}

@@

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="The time domain distributed as linear granularities $B$, $G'$, $H'$ and quasi-circular granularities $Q(B, G')$ and $Q(B, H')$. Both $Q(B, G')$ and $Q(B, H')$ have repeating patterns unlike $G'$ or $H'$ and the patterns are guided by the distribution of $B$ within $G'$ and $H'$ within a period shown by the hashed arrow."}
knitr::include_graphics("Figs/quasi-circular-ex.png")
```

@@

Aperiodic cyclic granularities are defined using aperiodic linear granularities. Consider n aperiodic linear granularities $M_i$  $\forall \{i\in{1, 2, \dots, n\}}$ such that \ref{def:periodical} does not hold true for them with respect to $B$ (the bottom granularity). <!--that is, none of them can be expressed as periodic or quasi-periodic with respect to the bottom granularity.--> However, $B \trianglelefteq M_i$ $\forall \{i\in{1, 2, \dots, n\}}$. Then according to Definition \ref{def:groupsinto}, for each index $j$ there exists a (possibly infinite) subset $T_{\{i_j\}}$ of the integers such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$ and suppose $M = \bigcup_{i=1}^{n}M_{i}$ is formed by collecting the granules of $\{M_1, M_2, \dots, M_n\}$. Here, index ${\{i_j\}}$ stands for the $j^{\text{th}}$ granule of the $i^{\text{th}}$ linear aperiodic granularity.

@@

**Example**: \autoref{fig:aperiodic-example} shows two aperiodic linear granularity $M_1$ and $M_2$. <!--Each granule is represented by a box. The diagram also illustrates that the granules that overlap share elements from the underlying time domain. -->The first slot in the diagram shows the index set and $A_{B, M}$ consists of three categories, $L(1)$ corresponding to the first aperiodic event $M_1$, $L(2)$ corresponding to aperiodic event $M_2$ and the $L(0)$ corresponding to no event/aperiodic linear granularity.

@@

**Order** of a linear granularity can be comprehended as the level of coarseness associated with a linear granularity. For two linear granularities $G$ and $H$, if $G$ groups into $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.

@@

```{r tab-mayan}
table_mayan <- tibble(G = c("kin", "uinal", "tun", "katun", "baktun"),
                      C = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                      K = c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      caption = "Hierarchy table for Mayan calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All cyclic granularities are circular with $K$ as the period length.")
```

@@

**Example:** Let us use Equation \ref{eq:eq7} to compute the multiple-order-up granularity uinal_katun for Mayan calendar.

@@

kable(table_greg, 
      caption = "Illustrative hierarchy table for Gregorian calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All these cyclic granularities are circular with $K$ as the period length except for day-of-month which is quasi-circular.")
```

@@

  knitr::kable(smart_data,
               caption = "Smart meter data structure with electricity demand for 50 households from SGSC project for every 30 minutes from 2012 to 2014.")
```

@@

```{r search_gran_limit2, echo=FALSE, eval = FALSE}
smart_meter10 %>% search_gran(
  highest_unit = "month",
  filter_out = c("hhour", "fortnight")
)%>% knitr::kable()
```

@@

  knitr::kable(smart_harmony,
                caption = "Harmonies with two cyclic granularity one placed on the facet and the other on x-axis with the corresponding levels. Out of 30 possible combinations of cyclic granularities that could be plotted only 13 are harmonies.")
```

@@

```{r hierarchy-cric}
library(gravitas)
library(tibble)
hierarchy_model <- tibble::tibble(
  G = c("over", "inning", "match", "season"),
  C = c("over-of-inning", "inning-of-match", "match-of-season", 1),
  K = c(20, 2, "k(match, season)", 1)
)
knitr::kable(hierarchy_model,
             caption = "Hierarchy table for cricket where each over is nested within innings, innings is nested within match and so on. Cyclic granularity over-of-inning, inning-of-match are assumed to be circular which means each inning will have 20 overs and each match has 2 innings and  match-of-season is assumed to be quasi-periodic. ")
```

>>>>

Linear time granularities respect the linear progression of time and are non-repeating such as hours, days, weeks and months. One of the first attempts to characterize these granularities is due to @Bettini1998-ed. However, the definitions and rules defined are inadequate for describing cyclic or repeating granularities. Hence, there is a need to define some new cyclic time granularities, that can be useful in visualizations. Cyclic time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

The remainder of the paper is organized as follows: Section \ref{sec:linear-time} provide some background material on linear granularities and introduces calendar algebra for computing different linear granularities. Section \ref{sec:cyclic-gran} formally characterizes different cyclic time granularities by extending the framework of linear time granularities. Section \ref{sec:cyclic-calendar} introduces cyclic calendar algebra for computing cyclic time granularities. Section \ref{sec:data-structure} discusses the data structure for exploring the conditional distributions of the associated time series across pairs of cyclic time granularities. Section \ref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization. Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application. Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.

@@

\begin{definition}[Finer than]\label{def:finerthan}
A linear granularity $G$ is finer than a linear granularity $H$, denoted $G \preceq H$, if for each index $i$, there exists an index $j$ such that
\[
G(i) \subset H(j).
\]
\end{definition}.

@@

For example, $day \trianglelefteq week$ and $day \preceq week$ since every granule of "week" is the union of some set of granules of "day" and each "day" is a subset of a "week". Consider another example where $day \trianglelefteq month$. This relationship however is incomplete without its association to periodicity. Each month is a grouping of the same number of days over years, hence the period of the grouping (day, month) is one year, if leap years are ignored. The period becomes 400 years with the inclusion of leap years and all their exceptions.

@@

Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra [@Ning2002-tf]. It is assumed that there exists a _bottom granularity_ and calendar algebra operations are designed to generate new granularities recursively from the bottom one. Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} for illustrations in circular and quasi-circular granularities.

@@

The altering-tick operation: 
: Let $G_1$, $G_2$ be full-integer labeled granularities, and $l$, $k$, $m$ integers, with $G_1 \trianglelefteq G_2$, $G_1\preceq G_2$, and $1 \leq l \leq m$. The altering-tick operation $\text{Alter}^{m}_{l,k} (G_2, G_1)$ operation modifies the granules of $G_1$ so that the $l^{\text{th}}$ granule of each period has $k$ additional granules of $G_2$.

For example, due to the uneven length of months, we need to use the altering-tick operation to compute months from days. We can consider a granularity "pseudomonth" which computes months only for non-leap years by grouping 31 days, and then shrink April, June, September and November by 1 day, and shrink February by 3 days [@Ning2002-tf]. For more variations of calendar algebra operations, see @Ning2002-tf.

@@

We propose a formalism of cyclic time granularities through the tsibble [@wang2019tsibble] data structure. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. <!--In a tsibble, each observation (row) is uniquely identified by index and key.--> A time domain, as defined by @Bettini1998-ed, is essentially a mapping of the index set to the index of a tsibble. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble.<!--Consistent with the assumption of @Bettini2000-vy, all linear granularities can be generated from the bottom granularity by calendar algebraic operations.-->

Cyclic granularities can be constructed by relating two linear granularities. The mappings between these linear granularities could be either _regular_ or _irregular_ with every granule of coarser linear granularity being made up of same (regular) or different (irregular) number of granules of finer linear granularity. <!--For example, a regular mapping exists between  (where 60 minutes always add up to 1 hour), while an irregular mapping exists between  (as the number of days per month ranges from 28 to 31). A grouping operation in Calendar algebra could lead to a regular mapping, whereas a altering-tick operation could result in an irregular mapping.--> Cyclic time granularities are referred to as **circular** if mappings are regular and **quasi-circular** if the mappings are irregular. Examples of common circular granularities include hour of the day, and day of the week, whereas examples for quasi-circular granularities can be day of the month or week of the month.

@@

\autoref{fig:circular-dow} depicts the circular granularity "Day-of-Week", constructed from linear granularities "day" (the bottom granularity) and "week". The granules that overlap share elements from the underlying time domain. In this example, $P=7$, and the circular granularity $C_{\text{day}, \text{week}}$ representing Day-of-Week consists of the repeated pattern $\{L(0), L(1), L(2),$ $L(3), L(4), L(5), L(6)\}$.

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
circular granularity && expression  && period length\\
\hline
minute-of-hour & $C_1$ & $= L_1(z \mod 60)$  & $P_1 = $&$60$ \\
minute-of-day & $C_2$ & $= L_2(z \mod 60*24)$  & $P_2=$&$`r 60*24`$\\
hour-of-day & $C_3$ & $= L_3(\lfloor z/60\rfloor\mod 24)$  & $P_3 =$&$24$ \\
hour-of-week & $C_4$ & $= L_4(\lfloor z/60\rfloor\mod 24*7)$  & $P_4=$&$`r 24*7`$\\
day-of-week & $C_5$ & $= L_5(\lfloor z/24*60\rfloor \mod 7)$  & $P_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative circular granularities with bottom granularity "minutes". Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and $P_i$ represents the period length.}
\label{tab:definitions}
\end{table}

<!-- ```{r tab-circular} -->
<!--  table_mayan <-  -->
<!--   tibble(C = c("minute-of-hour", -->
<!--                                     "minute-of-day",  -->
<!--                                     "hour-of-day", -->
<!--                                     "hour-of-week", -->
<!--                                     "day-of-week"), -->
<!--                        Expression = c("\$L\_1(z \mod 60)\$", -->
<!--                                         "\$L\_2(z \mod 60*24)\$", -->
<!--                                         "\$L\_3(\lfloor z/60\rfloor\mod 24)\$", -->
<!--                                         "\$L\_4(\lfloor z/60\rfloor\mod 24*7)\$", -->
<!--                                         "\$L\_5(\lfloor z/24*60\rfloor \mod 7)\$")) -->

<!--  kable(table_mayan, -->
<!--        format = "latex", -->
<!--        caption = "Hierarchy table for Mayan calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All cyclic granularities are circular with $K$ as the period length.") -->
<!-- ``` -->

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
quasi-circular granularity && potential period lengths\\
\hline
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative quasi-circular granularities $Q_i$ with potential period lengths $P_i$. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping and hence can not be expressed through modular arithmetic.}
\label{tab:quasi}
\end{table}

@@

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="The time domain distributed as linear granularities $B$, $G'$, $H'$ and quasi-circular granularities $Q(B, G')$ and $Q(B, H')$. Both $Q(B, G')$ and $Q(B, H')$ have repeating patterns unlike $G'$ or $H'$ and the patterns are guided by the distribution of $B$ within $G'$ and $H'$ within a period shown by the hashed arrows."}
knitr::include_graphics("Figs/quasi-circular-ex.png")
```

@@

Aperiodic cyclic granularities are defined using aperiodic linear granularities. Consider n aperiodic linear granularities $M_i$  $\forall \{i\in{1, 2, \dots, n\}}$ such that Definition \ref{def:periodical} does not hold true for them with respect to $B$ (the bottom granularity). <!--that is, none of them can be expressed as periodic or quasi-periodic with respect to the bottom granularity.--> However, $B \trianglelefteq M_i$ $\forall \{i\in{1, 2, \dots, n\}}$. Then according to Definition \ref{def:groupsinto}, for each index $j$ there exists a (possibly infinite) subset $T_{\{i_j\}}$ of the integers such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$. Suppose $M = \bigcup_{i=1}^{n}M_{i}$ is formed by collecting the granules of $\{M_1, M_2, \dots, M_n\}$. Here, index ${\{i_j\}}$ stands for the $j^{\text{th}}$ granule of the $i^{\text{th}}$ linear aperiodic granularity.

@@

**Example**: \autoref{fig:aperiodic-example} shows two aperiodic linear granularity $M_1$ and $M_2$. <!--Each granule is represented by a box. The diagram also illustrates that the granules that overlap share elements from the underlying time domain. -->The first slot in the diagram shows the index set and $A(B, M)$ consists of three categories, $L(1)$ corresponding to the first aperiodic event $M_1$, $L(2)$ corresponding to aperiodic event $M_2$ and the $L(0)$ corresponding to no event/aperiodic linear granularity.

@@

**Order** of a linear granularity can be comprehended as the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ groups into $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.

@@

```{r tab-mayan}
table_mayan <- tibble(G = c("kin", "uinal", "tun", "katun", "baktun"),
                      C = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                      K = c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      booktabs = TRUE,
      caption = "Hierarchy table for Mayan calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All cyclic granularities are circular with $K$ as the period length.")
```

@@

**Example:** Let us use Equation \ref{eq:eq7} to compute the multiple-order-up granularity $C_{uinal,katun}$ for Mayan calendar.

@@

kable(table_greg, 
      format = "latex",
      booktabs = TRUE,
      caption = "Illustrative hierarchy table for Gregorian calendar. $G$ and $C$ represent the linear and single order-up cyclic granularities respectively. All these cyclic granularities are circular with $K$ as the period length except for day-of-month which is quasi-circular.")
```

@@

  knitr::kable(smart_data,
               format = "latex",
               booktabs = TRUE,
               caption = "Smart meter data structure with electricity demand for 50 households from SGSC project for every 30 minutes from 2012 to 2014.")
```

@@

```{r search_gran_limit2, echo=FALSE, eval = FALSE}
smart_meter10 %>% search_gran(
  highest_unit = "month",
  filter_out = c("hhour", "fortnight"))%>%
  knitr::kable(format = "latex",
      booktabs = TRUE)
```

@@

  knitr::kable(smart_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with two cyclic granularity one placed on the facet and the other on x-axis with the corresponding levels. Out of 30 possible combinations of cyclic granularities that could be plotted only 13 are harmonies.")
```

@@

```{r hierarchy-cric}
library(gravitas)
library(tibble)
hierarchy_model <- tibble::tibble(
  G = c("over", "inning", "match", "season"),
  C = c("over-of-inning", "inning-of-match", "match-of-season", 1),
  K = c(20, 2, "k(match, season)", 1)
)
knitr::kable(hierarchy_model,
             format = "latex",
             booktabs = TRUE,
             caption = "Hierarchy table for cricket where each over is nested within innings, innings is nested within match and so on. Cyclic granularity over-of-inning, inning-of-match are assumed to be circular which means each inning will have 20 overs and each match has 2 innings and  match-of-season is assumed to be quasi-periodic. ")
```
